% !TEX program = pdflatex
\input{jmlr_coverletter_preamble.tex}

\begin{document}
Journal of Machine Learning Research \hfill \today

\bigskip

Dear Editors:

We are writing to submit our manuscript ``An Embedding Framework for the Design and Analysis of Consistent Polyhedral Surrogates'' to the \emph{Journal of Machine Learning Research (JMLR)}.

Our manuscript proposes a new framework to design consistent convex surrogates for general discrete prediction tasks.
As convex surrogates are often designed in an ad-hoc manner, and often are inconsistent for the desired target task, our framework fills a urgent gap in the literature.

Our manuscript extends the conference publication \emph{An Embedding Framework for Consistent Polyhedral Surrogates} (NeurIPS 2019) and incorporates roughly half the results from \emph{Surrogate Regret Bounds for Polyhedral Losses} (NeurIPS 2021).
We have substantially rewritten and reorganized these papers, streamlined the presentation, adjusted the core definitions slightly to make the results more intuitive and elegant, etc., all with the goal of laying out the definitive version of the embedding framework.
We also added entirely new examples and results (\S 5, \S 6, \S 7, \S E).
For example, \S 6 shows the equivalence of several natural notions of non-redundancy, and \S 7 uses our framework to show that indirect elicitation is equivalent to consistency for polyhedral surrogates.

We suggest the following action editors, referees, and keywords for our submission.

Action Editors:
\begin{itemize}
    \item Ambuj Tewari, University of Michigan (\url{tewaria@umich.edu})
    \item Sanmi Koyejo, University of Illinois at Urbana-Champaign (\url{sanmi@illinois.edu})
    \item Moritz Hardt, Max Planck Institute for Intelligent Systems, T\"ubingen (\url{hardt@is.mpg.de})
    \item Tong Zhang,  The Hong Kong University of Science and Technology (\url{tongzhang@tongzhang-ml.org})
\end{itemize}

Reviewers:
\begin{itemize}
    \item Bob Williamson, University of T\"ubingen (\url{bob.williamson@uni-tuebingen.de})
    \item Shivani Agarwal, University of Pennsylviania (\url{ashivani@seas.upenn.edu})
    \item Alex Nowak-Vila, Owkin (\url{alex.nowak-vila@inria.fr})
    \item Clayton Scott, University of Michigan (\url{clayscot@umich.edu})
    \item Harish Ramaswamy, IIT Madras (\url{hariguru@cse.iitm.ac.in})
      % \item Pranjal Ashwathi (see recently published ICML paper) <-- could be great, but I'd have to look into their work more; seemed more on the PAC learning side at first glance, but lots of "consistency" and "surrogates" so maybe a good fit
      % These are either too much of a stretch or too junior I think -- journal reviewers are usually more senior, though students definitely do it now and then.  FWIW, Han is junior faculty now, though agreed.
    % \item Yutong Wang
    % \item Han Bao, University of Tokyo / RIKEN AIP (first.lastname@institution.edu)
    % \item Authors of this paper: \url{https://arxiv.org/pdf/2202.02193.pdf} -- bit of a stretch
    % \item Satyen Kale
\end{itemize}

Keywords: Statistical consistency, surrogate loss functions, calibration, property elicitation, embeddings.

We confirm that none of the co-authors listed below have a conflict of interest with the action editors and referees suggested above.
(Bob Williamson was a member of the first author's dissertation committee but we did not consider that a conflict.)
All co-authors consent to this submission to JMLR.

\bigskip

Sincerely,

\medskip

Jessie Finocchiaro (University of Colorado Boulder), corresponding author\\
Rafael Frongillo (University of Colorado Boulder)\\
Bo Waggoner (University of Colorado Boulder)

\end{document}






































